## NCAA Football Attendance 

Let's load the tidyverse.

```{r}
library(tidyverse)
```

And read in the attendance data:

```{r}
attendance <- read_csv("https://dwillis.github.io/sports-data-files/attendance.csv")
```

Using the tidyverse's `pivot_longer` function, turn the currently wide data into longer data and save it as a new dataframe called `attendance_longer`:

```{r}
attendance_longer <- attendance %>% pivot_longer(cols = starts_with("20"), names_to = "Year", values_to = "Attendance")
```

Let's try to figure out whether football attendance has returned to "normal" by 2022, defining "normal" as 2019 figures. For that we'll need to isolate those two years using `filter()` and get rid of any NAs:

```{r}
attendance_two_years <- attendance_longer |> filter(Year == 2019 | Year == 2022) %>% na.omit()
```

Now, in order to calculate a percentage change between those two years, we'll need to go back to wider data and again ditch teams where we don't have both years:

```{r}
attendance_wide <- attendance_two_years |> pivot_wider(names_from = Year, values_from = Attendance) %>% na.omit()
```

Finally, we'll add a percentage change column to that dataframe (remember, it's (New-Old)/Old) and arrange it to see the results.

```{r}
attendance_wide <- attendance_wide |> mutate(percent_change = (`2022`-`2019`)/`2019`*100) %>% 
  arrange(desc(percent_change))
```

Some of these clearly are influenced by performance on the field. Below, describe the most interesting results (positive or negative) and what you think might be going on with them. Feel free to do some googling and describe what other data would be helpful to clarify what the best stories here might be. What surprises you about these results?

**ANSWER**

One of the most interesting cases that I see is that Georgia, who won the national championship in 2021, ranked 100 out of 126 in terms of attendance increase. UGA had an attendance drop of about 14% from 2019 to 2022, a season after they won the National Championship. This is extremely strange to me because it would make sense that Georgia's numbers would go up after winning the school's first national championship since 1980 and not down. Georgia always plays one neutral site game per year against Florida, but played 2 in 2022 (vs Oregon in Atlanta Week 1). This might explain some of the numbers, but it is still pretty baffling to see Georgia so low on this list. 


Another interesting case on this list is the Indiana Hoosiers. Known for being a basketball school, Indiana had a really good 2020 season following a 7-5 season in 2019. Unfortunately for Indiana fans, they were unable to go see their team play in 2020 thanks to Covid. Jn 2022, Indiana was one of the worst teams in the Big Ten. After winning their first three games against Illinois, Idaho, and Western Kentucky, Indiana won only once more the rest of the way finishing the season with a 4-8 record and 2-7 in the conference. Despite that, Indiana had the 6th highest attendance percent increase from 2019 to 2022 at 32%. 



I was also a but surprised where Maryland landed on this list. I would have expected the Terps numbers to have gone up a little bit. 2019 was the first year of Mike Locksley's tenure and Maryland has steadily improved every year since he has been here. Last year, Maryland went 7-5 not including the school's second straight bowl win in the Duke's Mayo Bowl over NC State. I would hace expected the Terps attendance to have gone up last year. Despite that, Maryland still ranks ahead of several elite college football programs such as Alabama, Wisconsin, Texas A&M, Washington, and Oregon. 

