## The question that I plan to tackle is: I want to know which pitch is baseball is the hardest to hit, and more specifically, which specific pitcher’s specific pitch is hardest to hit. For this I will need data on ball spin rates, RPMs, as well as league stats. 

## I believe that pitch by pitch data exists from this MLB season and do not believe I will need assistance in getting the data. I do believe that I might need help in making the data to a convertable format for R. I do not believe that I will need to improve the data as long as the data has the results of each at-bat. 


## Here is where I found the initial data to use for my questions: https://www.retrosheet.org/game.htm 

## I believe that once I figure out how to convert this data into a file that I can use, my data will be effective. 

```{r}
if (!requireNamespace('devtools', quietly = TRUE)){
  install.packages('devtools')
}
devtools::install_github(repo = "BillPetti/baseballr")


```
```{r}
library(tidyverse)
library(baseballr)
library(devtools)
library(dplyr)

```


```{r}
pitchers<-bref_daily_pitcher("2023-03-30", "2023-10-01") %>% 
  fip_plus() %>% 
  dplyr::select(season, Name, IP, ERA, SO, uBB, HBP, HR, FIP, wOBA_against, wOBA_CON_against) %>%
  dplyr::arrange(dplyr::desc(IP)) 
  

```



```{r}
hitters <- bref_daily_batter("2023-03-30", "2023-10-01") 
hitters %>%
  dplyr::glimpse()
```
## I was able to load the data for hitters and pitchers. While I do not believe that this package has any way for me to answer the questions I intitally had, I can come up with other questions that I can talk about with baseball. 

## For example,

## Does the team that has the highest OPS's (on base + slugging), have the most wins?
## Does age coorelate at all with better hitting stats?

## There are probably more and better questions I can think of, but those are two examples just to start of with.
