```{r}
library(tidyverse)
```

```{r}
volleyballstats<-read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2023.csv")
```
# Loading the data 
```{r}
volleyball_eqaulity <- volleyballstats |> 
  select(team, kills, defensive_kills, errors, defensive_errors)
```
# I decieded to use kills and errors to get my z-score table. 
```{r}
volleyballtotals <- volleyball_eqaulity |> 
  group_by(team) |> 
  summarise(
    killsAvg = mean(kills), 
    defensive_killsAvg = mean(defensive_kills), 
    errorsAvg = mean(errors),
    defensive_errorsAvg = mean(defensive_errors)
    ) 
```
# Getting averages 
```{r}
teamzscore <- volleyballtotals |> 
  mutate(
    killszscore = as.numeric(scale(killsAvg, center = TRUE, scale = TRUE)),
    defensive_killszscore = as.numeric(scale(defensive_killsAvg, center = TRUE, scale = TRUE)),
    errorszscore = as.numeric(scale(errorsAvg, center = TRUE, scale = TRUE)) * -1,
    defensive_errorszscore = as.numeric(scale(defensive_errorsAvg, center = TRUE, scale = TRUE)) * -1,
    TotalZscore = killszscore + defensive_killszscore + errorszscore + defensive_errorszscore)
```
# getting the z-score for each category 
```{r}
head(teamzscore)
```
```{r}
teamzscore |> arrange(desc(TotalZscore))
```
```{r}
teamzscore |> 
  filter(team == "Maryland Terrapins, Terps") |> 
  arrange(desc(TotalZscore)) |>
  select(team, TotalZscore)
```

# We see that from the data, that kills and errors are not factors that we can use to try and predict a volleyball game. The teams that are ranked the highest on this list are teams that typically do not have the most success in the sport. This is pretty interesting because in order to win volleyball games, you need to make kills. The fact that teams that have a lot of success in the sport (teams that are in the Big Ten) are not higher on this list. Maryland is found towards the middle of this data. 
