---
title: "Women's Soccer Data"
output: html_notebook
---

We'll use this notebook to explore some NCAA women's soccer data and [our questions](https://docs.google.com/spreadsheets/d/1kTSrnl1URmcexIWLDMWqDnp3q-c2OS45uifnhjp10n4/edit#gid=0). First, let's load the tidyverse library:

```{r}
library(tidyverse)
```

We'll want to start with 2023 match data, which is located in [this GitHub repository](https://github.com/dwillis/NCAAWomensSoccerData). We can load the match data directly from GitHub using `read_csv`:


```{r}
matches_2022 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2022.csv")
```

Let's take a look at this data to see what it contains, using `head` and `glimpse`:

```{r}
head(matches_2023)
glimpse(matches_2023)
```

Now, onto the questions using aggregates, which means `group_by` and `summarize`:

1. How many shots in total has Maryland attempted and how many have been on goal? Calculate a percentage of shots on goal.

```{r}
matches_2023 %>% 
filter(team == "Maryland Terrapins, Terps") %>% 
summarise(team, sh_att, so_g,
      total_shots = sum(sh_att),
      total_sog = sum(so_g),
      percentage = (total_shots/total_sog))


 


```

2. What about the same shot stats from last season's first four games? You'll need to load the matches from 2022 - just change the season in the URL - and filter by date to find the first four games.

```{r}
matches_2022 %>% 
summarise(date, team, sh_att, so_g,
      total_shots = sum(sh_att),
      total_sog = sum(so_g),
      percentage = (total_shots/total_sog)) %>% 
  filter(team == "Maryland Terrapins, Terps")




```
# I know there is a way to use slice max to only show the results for the first four games, I just cannot remember how to use it. 



3. What about draws - Maryland started 2022 with 4 ties. Have any other teams had as many this season?

```{r}
matches_2023 %>% 
  summarise(team, outcome
            ) 



```


4. How many total corner kicks has Maryland had so far and how many have its opponents have? Calculate the difference between the two totals for every team.

```{r}
matches_2023 %>% 
  summarise(team, opponent, corners, defensive_corners,
            difference = defensive_corners - corners) %>% 
  filter(team == "Maryland Terrapins, Terps") 
  
 



```

