---
title: "Women's Soccer Data"
output: html_notebook
---

We'll use this notebook to explore some NCAA women's soccer data and [our questions](https://docs.google.com/spreadsheets/d/1kTSrnl1URmcexIWLDMWqDnp3q-c2OS45uifnhjp10n4/edit#gid=0). First, let's load the tidyverse library:

```{r}
library(tidyverse)
```

We'll want to start with 2023 match data, which is located in [this GitHub repository](https://github.com/dwillis/NCAAWomensSoccerData). We can load the match data directly from GitHub using `read_csv`:


```{r}
matches_2022 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2022.csv")

matches_2023 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2023.csv")
```

Let's take a look at this data to see what it contains, using `head` and `glimpse`:

```{r}
head(matches_2023)
glimpse(matches_2023)
```

Now, onto the questions using aggregates, which means `group_by` and `summarize`:

1. How many shots in total has Maryland attempted and how many have been on goal? Calculate a percentage of shots on goal.

```{r}
matches_2023 %>% 
filter(team == "Maryland Terrapins, Terps") %>% 
summarise(team, sh_att, so_g,
      total_shots = sum(sh_att),
      total_sog = sum(so_g),
      percentage = (total_shots/total_sog))


 


```

2. What about the same shot stats from last season's first four games? You'll need to load the matches from 2022 - just change the season in the URL - and filter by date to find the first four games.

```{r}
matches_2022 %>% 
summarise(date, team, sh_att, so_g,
      total_shots = sum(sh_att),
      total_sog = sum(so_g),
      percentage = (total_shots/total_sog)) %>% 
  filter(team == "Maryland Terrapins, Terps")




```
# I know there is a way to use slice max to only show the results for the first four games, I just cannot remember how to use it. 



3. What about draws - Maryland started 2022 with 4 ties. Have any other teams had as many this season?

```{r}
matches_2023 %>% 
  summarise(team, outcome
            ) 



```


4. How many total corner kicks has Maryland had so far and how many have its opponents have? Calculate the difference between the two totals for every team.

```{r}
matches_2023 %>% 
  summarise(team, opponent, corners, defensive_corners,
            difference = defensive_corners - corners) %>% 
  filter(team == "Maryland Terrapins, Terps") 
  
 



```


# Significance Tests

Hypothesis: There is more scoring in women's soccer this season than last season

Add a column to both dataframes that contains the total_goals for each match. To do this, we'll use mutate and we will save the results back to the same dataframe. 


```{r}
matches_2022 <- matches_2022 %>% 
  mutate(total_goals = goals + defensive_goals)


matches_2023 <- matches_2023 %>% 
  mutate(total_goals = goals + defensive_goals)


```


```{r}

t.test(matches_2022$total_goals, matches_2023$total_goals)


```

Both numbers are very similar but so far in 2023, there are about .3 more goals being scored than 2022. The p value is very well below .05 so therefore we reject the null hypothesis. The evidence shows that our hypothesis, that there are more goals being scored this year, is correct. 




```{r}

matches_2022_early <- matches_2022 %>% 
  filter(date < '2022-09-14')


```



```{r}

t.test(matches_2022_early$total_goals, matches_2023$total_goals)



```


At this time last year, our data shows that the amount of goals scored was about the same as the amount of goals per game that have been scored thus far in the 2023 season. It appears that as the season went on the number of goals per game dropped a bit. This is likely because when schools begin conference play, which usually features harder oppoenents than non-conference play for power 5 schools, the level of competition is raised a bit and there might be less goals per game because of that.






